# Accuraccy results

Here we report the accuracy for **final pipeline returned from a TPOT2 run** on each OpenML task.
40 replicates were conducted for each evaluation strategy explored.

## Analysis setup

```{r exp-data-setup, message=FALSE}
library(ggplot2)
library(cowplot)
library(dplyr)
library(PupillometryR)

NAMES <- c("10-fold cv","90/10","70/30","50/50")
TSIZE <- 22
data_dir <- "./"
task_id_lists <- c(167104, 167184, 167168, 167161, 167185, 189905)

scores <- read.csv("./scores.csv", header = TRUE, stringsAsFactors = FALSE)
scores$acro <- factor(scores$acro, levels = NAMES)
```

## Accuracy per OpenML task

Accuracy of the returned pipeline from an evolutionary run.

### Task 167104


```{r task-1-plt, warning=FALSE, out.width="100%"}
filter(scores, taskid == task_id_lists[1]) %>%
  ggplot(., aes(x = acro, y = accuracy, color = acro,
                fill = acro, shape = acro)) +
  geom_flat_violin(position = position_nudge(x = 0.1, y = 0),
                   scale = "width", alpha = 0.2, width = 1.5) +
  geom_boxplot(color = "black", width = .08, outlier.shape = NA, alpha = 0.0,
               size = 0.8, position = position_nudge(x = .15, y = 0)) +
  geom_point(position = position_jitter(width = .015, height = .0001),
             size = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name = "Accuracy %",
    breaks = c(.74, .78, .82, .86),
    labels = scales::percent

  ) +
  scale_x_discrete(
    name = "Treatment"
  ) +
  scale_shape_manual(values = SHAPE) +
  scale_colour_manual(values = cb_palette, ) +
  scale_fill_manual(values = cb_palette) +
  ggtitle("Accuracy") +
  p_theme
```

Summary statistics for the generation a satisfactory solution is found.

```{r task-1-sum}
performance <- filter(scores, taskid == task_id_lists[1])
performance %>%
  group_by(acro) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(accuracy)),
    min = min(accuracy, na.rm = TRUE),
    median = median(accuracy, na.rm = TRUE),
    mean = mean(accuracy, na.rm = TRUE),
    max = max(accuracy, na.rm = TRUE),
    IQR = IQR(accuracy, na.rm = TRUE)
  )
```

Kruskal–Wallis test illustrates evidence of statistical differences.

```{r task-1-kru}
kruskal.test(accuracy ~ acro, data = performance)
```

Results for post-hoc Wilcoxon rank-sum test with a Bonferroni correction.

```{r task-1-wil}
pairwise.wilcox.test(x = performance$accuracy, g = performance$acro,
                     p.adjust.method = "bonferroni",
                     paired = FALSE, conf.int = FALSE, alternative = "t")

```