---
title: "Supplemental Material for 'Lexidate: Model Evaluation and Selection with Lexicase Selection'"
author: "Anonymous GECCO"
date: "`r Sys.Date()`"    
output: bookdown::gitbook
documentclass: book
bibliography: ["packages.bib", "supplemental.bib"]
biblio-style: apalike
nocite: '@*'
link-citations: yes
github-repo: jgh9094/GECCO-2024-LEXIDATE-EVALUATION
description: "Supplemental material"
---

```{r index, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, include=FALSE, echo=TRUE}
library(ggplot2)
library(cowplot)
library(dplyr)
library(PupillometryR)

NAMES <- c("10-fold cv","90/10","70/30","50/50")
SHAPE <- c(21,24,22,25)
cb_palette <- c('#D81B60','#1E88E5','#FFC107','#004D40')
TSIZE <- 22
task_id_lists <- c(167104, 167184, 167168, 167161, 167185, 189905)

p_theme <- theme(
  plot.title = element_text( face = "bold", size = 22, hjust=0.5),
  panel.border = element_blank(),
  panel.grid.minor = element_blank(),
  legend.title=element_text(size=22),
  legend.text=element_text(size=23),
  axis.title = element_text(size=23),
  axis.text = element_text(size=19),
  legend.position="bottom",
  panel.background = element_rect(fill = "#f1f2f5",
                                  colour = "white",
                                  size = 0.5, linetype = "solid")
)
```

# Introduction

This is not intended as a stand-alone document, but as a companion to our manuscript.

## About our supplemental material

As you may have noticed (unless you're reading a pdf version of this), our supplemental material is hosted using [GitHub pages](https://pages.github.com/).
We compiled our data analyses and supplemental documentation into this nifty web-accessible book using [bookdown](https://bookdown.org).

<!-- The source code/configuration files for this supplemental material can be found in [this GitHub repository](https://github.com/amlalejini/GECCO-2024-phylogeny-informed-subsampling). -->

Our supplemental material includes the following:

Hello world

<!-- - Data availability (Section \@ref(data-availability)) -->
<!-- - Local compilation (Section \@ref(local-compilation)) -->
<!-- - GP instruction set (Section \@ref(signalgp-instruction-set)) -->
  <!-- - Selection scheme diagnostics (Section \@ref(selection-scheme-diagnostic-experiments))
  - Program synthesis problems (Section \@ref(program-synthesis-experiments)) -->

<!-- ## Contributing authors -->

<!-- - Alexander Lalejini -->
<!-- - Marcos Sanson -->
<!-- - Jack Garbus -->
<!-- - Emily Dolson -->