---
title: "Supplemental Material for 'Lexidate: Model Evaluation and Selection with Lexicase Selection'"
author: "Anonymous GECCO"
date: "`r Sys.Date()`"
output: bookdown::gitbook
documentclass: book
bibliography: ["packages.bib", "supplemental.bib"]
biblio-style: apalike
nocite: '@*'
link-citations: yes
github-repo: jgh9094/GECCO-2024-LEXIDATE-EVALUATION
description: "Supplemental material"
---

```{r index, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, echo=TRUE}
library(ggplot2)
library(cowplot)
library(dplyr)
library(PupillometryR)
library(scales) # to access break formatting functions


NAMES <- c("10-fold cv","90/10","70/30","50/50")
SHAPE <- c(21,24,22,25)
cb_palette <- c('#D81B60','#1E88E5','#FFC107','#004D40')
TSIZE <- 22
task_id_lists <- c(167104, 167184, 167168, 167161, 167185, 189905)

p_theme <- theme(
  plot.title = element_text( face = "bold", size = 22, hjust=0.5),
  panel.border = element_blank(),
  panel.grid.minor = element_blank(),
  legend.title=element_text(size=20),
  legend.text=element_text(size=20),
  axis.title = element_text(size=20),
  axis.text = element_text(size=19),
  legend.position="bottom",
  panel.background = element_rect(fill = "#f1f2f5",
                                  colour = "white",
                                  size = 0.5, linetype = "solid")
)
```

# Introduction

This is not intended as a stand-alone document, but as a companion to our manuscript.

## About our supplemental material

As you may have noticed (unless you're reading a pdf version of this), our supplemental material is hosted using [GitHub pages](https://pages.github.com/).
We compiled our data analyses and supplemental documentation into this nifty web-accessible book using [bookdown](https://bookdown.org).

The code used for this supplemental material can be found in [this GitHub repository](https://github.com/jgh9094/GECCO-2024-LEXIDATE-EVALUATION).

Our supplemental material includes the following:

- Accuracy results (Section \@ref(accuracy-results))
- Complexity results (Section \@ref(complexity-results))

## Contributing authors

- [Jose Guadalupe Hernandez](https://jgh9094.github.io/)
- [Anil Kumar Saini](https://theaksaini.github.io/)
- [Jason H. Moore](https://jasonhmoore.org/)